---
title: "Logistic Regression Mini Proj"
output: html_notebook
---

# Exercise: logistic regression


**Use the NH11 data set that we loaded earlier.**

*Note that the data is not perfectly clean and ready to be modeled. You will need to clean up at least some of the variables before fitting the model.*

**1. Use glm to conduct a logistic regression to predict ever worked (everwrk) using age (age_p) and marital status (r_maritl).**

```{r echo=TRUE}
NH11 <- readRDS("NatHealth2011.rds")
labs <- attributes(NH11)$labels

nh11.wrk.age.mar <- subset(NH11, select = c("everwrk", "age_p", "r_maritl"))

summary(nh11.wrk.age.mar)

NH11 <- transform(NH11,
                  everwrk = factor(everwrk,
                      levels = c("1 Yes", "2 No")),
                  r_maritl = droplevels(r_maritl))

mod.wk.age.mar <- glm(everwrk ~ age_p + r_maritl, data = NH11,
                      family = "binomial")

summary(mod.wk.age.mar)
```

*In modeling "ever worked", it seems that "age_p", "widowed", "divorced", "never married" are the most significant indicators, followed by "living with partner". According to the summary generated coefficients, "age_p", "divorced", "separated", and "living with partner", were negatively associated with ever worked, meaning that higher values in these variables contribute to a lower probibility of ever working.* 

##   2. Predict the probability of working for each level of marital status.

```{r echo=TRUE}
install.packages("effects")
library(effects)
data.frame(Effect("r_maritl", mod.wk.age.mar))
plot(allEffects(mod.wk.age.mar))
```
*These plots confirm my interpretation from the coefficient summary above. I would like more clarification on what is meant by "everwork". The data frame effect table fit column indicates that a widow has the highest probability of "ever worked" at 19%, while a divorcee has the lowest probability  of "ever worked" at 5%.*
