---
title: "Logistic Regression Mini Proj"
output: html_notebook
---

## Exercise: logistic regression
## ───────────────────────────────────

##   Use the NH11 data set that we loaded earlier.

##   Note that the data is not perfectly clean and ready to be modeled. You will need to clean up at least some of the variables before fitting the model.

##   1. Use glm to conduct a logistic regression to predict ever worked (everwrk) using age (age_p) and marital status (r_maritl).

```{r}
NH11 <- readRDS("NatHealth2011.rds")
labs <- attributes(NH11)$labels

nh11.wrk.age.mar <- subset(NH11, select = c("everwrk", "age_p", "r_maritl"))

summary(nh11.wrk.age.mar)

NH11 <- transform(NH11,
                  everwrk = factor(everwrk,
                      levels = c("1 Yes", "2 No")),
                  r_maritl = droplevels(r_maritl))

mod.wk.age.mar <- glm(everwrk ~ age_p + r_maritl, data = NH11,
                      family = "binomial")

summary(mod.wk.age.mar)
```

##   2. Predict the probability of working for each level of marital status.

```{r}
install.packages("effects")
library(effects)
data.frame(Effect("r_maritl", mod.wk.age.mar))
plot(allEffects(mod.wk.age.mar))
```

